Caveat Emptor: light curves of the brightest stars in the \\ Southern sky as seen by bRing

### 2024-01-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {The brightest stars in the sky are also amongst the most difficult to obtain long-term precision photometry. }
  % aims heading (mandatory)
   {We provide high cadence light curves with an individual photometric precision of 0.5\% for 154 stars in the Southern hemisphere from the bRing robotic observatories.}
  % methods heading (mandatory)
   {We process the bRing images and remove the systematic trends due to the large pixel sizes, the varying night sky background, cloud coverage and intrapixel variations, in addition to diurnal, synodic and seasonal variations.}
  % results heading (mandatory)
   {We present 154 light curves for stars $m_V<4$ for all stars below $\delta \leq -30\degr $ covering baselines up to 3 years. The data is obtained by the $\beta$ Pictoris b Ring project (bRing), after which it is reduced and detrended.}
  % conclusions heading (optional), leave it empty if necessary 
   {}

@@

\begin{enumerate}
    \item All data points from the eastern Australian camera on 3 and 4 April 2018 and the eastern South African camera on 10 September 2020 were discarded due to significant outliers of unknown origin.
    \item The 2.35 second exposures were used.
    \item We used the astrometry and photometry flags of the daily data. 
    %
    These tell us if the measured flux is too high or too low to be realistic or if no photometry was performed due to, e.g., the star being too close to the edge of the image.
    %
    Only the data without any bad flags was used. 
    \item We made sure that the magnitude error for the daily data is always greater than zero and finite, so no incorrect values are encountered. 
    \item All data where the Sun is lower than $-18\degr$ was selected. %This was added to ensure that the sky background did not get too bright. 
    \item The data points where the cloud error was 3$\sigma$ above the mean cloud error were deleted.
    %
    The 3$\sigma$ cutoff was estimated by eye.
    %
    The cloud error tells us how the transmission changes over time; a big change might mean a cloud is in view.
    %
    These outliers usually indicate that the clouds are variable at that point in time, in which case the data should not be used.
\end{enumerate}

@@

\begin{itemize}
    \item The 5$\sigma$ outliers based on magnitude error were discarded. %A big error could mean that the measurement is wrong. 
    \item The 3$\sigma$ outliers for the mean of the clouds were also removed. %This results in less background noise.
    \item The final step was to reject the 5$\sigma$ outliers for the mean of the sky background. %This rejection also results in less background noise.
\end{itemize}

@@

The last trend we removed is the one caused by the moon, which changes the sky background.
%
Trends matched to the synodic period (29.5305 days) were fitted and removed.
%
%The synodic period of the moon\footnote{The synodic period of the moon is 29.530588853 days.} and 25 bins per day were used to find a sigma-clipped mean per bin. This mean was subtracted from the data points in the bin.

%For each step in the detrending process, the offsets calculated in the previous step were added.

At this stage, the light curve for each star has all known trends removed.

For variable stars with a known period, we removed the large amplitude periodic variations before carrying out the detrending listed ablove, and then added this offset back into the light curve after the reduction steps.

Examples of the detrending steps are shown in the figures below.

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Mimosa_detrend_steps.png}
%     \caption{This figure shows the steps for detrending a non-variable star. The first plot shows the data before detrending.
%     The second plot shows the data after detrending the LSTSEQ. The third plot shows the data after detrending per Julian Date. The final plot shows the data after detrending for the moon. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
%     \label{Mimosa_detrend_steps}
% \end{figure}
% %uitleg over figuren
% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Mimosa_detrending.png}
%     \caption{This figure shows the difference in the light curves before and after detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
%     \label{Mimosa_detrend}
% \end{figure}
% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Mimosa_detrending_zoom.png}
%     \caption{This figure shows the difference in the light curves before and after detrending on a daily scale. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The plot is zoomed in on the horizontal axis.}
%     \label{Mimosa_detrend_zoom}
% \end{figure}

After detrending we bin the data to make the light curves appear more smooth. Bins of 50 data points are used, to resemble the binning of the quarterly data. Binning is conducted based on LSTSEQ, which keeps count of the possible 13500 exposures per day. This means that if two data points were taken at very different times (for example, at the end of a day and at the beginning of the next day), these points will not be put into the same bin. For every 50 points, the mean magnitude is computed. This mean magnitude is inserted at the mean time interval of the data points.

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Mimosa_bin.png}
%     \caption{This figure shows the detrended data of a star before and after binning. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
%     \label{Mimosa_bin}
% \end{figure}

% \section{Searching for periodic signals}
% \label{sec:tlslomb}

% Using the cleaned light curves, a search for periodic signals can be done.
% %
% Two methods were used for this. The Transit Least Squares algorithm was used to find transits in the light curves and the Lomb-Scargle periodograms were used to find sinusoidal periodic signals in the data.

% Once a signal was found, a period fold was used to determine the validity of the signal. Using a period fold, the shape of the periodic behaviour can be found.

\section{Results}
\label{sec:results}
% Using the bRing cameras, the 157 brightest stars ($m_V < 4$) in the southern hemisphere were observed. After performing data reduction, the trends caused by external effects in the data were removed. This process is called detrending. We removed two daily trends and the monthly trend caused by the moon. After this, light curves of these stars were generated. Finally, periodic signals could be found using these light curves. If these signals appeared to be transits or eclipses, the Transit Least Squares algorithm \citep{Hippke_2019} was applied. For variable stars such as pulsating or rotating stars, Lomb-Scargle periodograms \citep{VanderPlas_2012} \citep{VanderPlas_2015} were used.

@@

@@

% \begin{enumerate}
% \item \ref{Canopus} shows the light curve of alpha Carinae, the second brightest star in the sky and the brightest star in the southern hemisphere. It is better known as Canopus. The light curve can be seen in.
% \item \ref{Rigil_Kentaurus} shows the light curve of alpha Centauri A, the third brightest stars in the sky. It is also known as Rigil Kentaurus. It is part of the alpha Centauri system, which contains Proxima Centauri, the closest star known to the Sun. 
% \item \ref{Achernar} presents the light curve of alpha Eridani, also known as Achernar.
% \item \ref{Hadar} shows the light curve of beta Centauri, also called Hadar. This star is a Beta Cephei.
% \item \ref{Acrux} presents the light curve of alpha Crucis, a binary star system also known as Acrux.
% \item \ref{Mimosa} shows the light curve of beta Crucis, also known as Mimosa.
% \item \ref{Shaula} shows the light curve of lambda Scorpii, also known as Shaula. This is a binary system, with a Beta Cephei as primary star.
% \item \ref{Gacrux} displays the light curve of gamma Crucis, also called Gacrux.
% \item \ref{Miaplacidus} shows the ninth brightest star, beta Carinae. It is also known as Miaplacidus.
% \item \ref{Alnair} shows the final brightest star. This is alpha Gruis, also known as Alnair.

@@

Two stars are very close to the Sun in the HR diagram in \ref{HRD}. These stars are delta Pavonis and Beta Hydri.
%
Delta Pavonis has a luminosity of 1.22 L$_\odot$ \citep{Bruntt_2010}, a mass of 0.991 M$_\odot$ and a radius of 1.22 R$_\odot$ \citep{2008yCat..21680297T}.
%
It is a subgiant star which will relatively soon start to become a red giant.
%
Beta Hydri has a luminosity of 3.49 L$_\odot$, a mass of 1.08 M$_\odot$ and a of radius 1.81 R$_\odot$ \citep{Brand_o_2011}.
%
Beta Hydri is also a subgiant star.

@@

\section{Discussion}
\label{sec:discussion}

157 light curves of the brightest stars ($m_V < 4$) in the southern hemisphere ($\delta \leq -30^o$) were created. This is the first time light curves have been produced for such bright stars. We discuss our results in the subsections below. Limitations and strengths of the methods used are given as well.

\subsection{Data reduction}
\label{sec:discdatared}
% The data reduction still has a few shortcomings.

@@

Intrapixel variations were neglected in the data reduction. These quasi-sinusoidal modulations are caused by the interline design of the CCDs \citep{Talens_2018}. The intrapixel variations cause noise in the light curves, but are too complex to remove in this research.

@@

After detrending the calibrated data, the mean magnitude of the stars is zero. For variable stars this is prevented by adding the offset of the period back into the detrended data. To fix the mean for the stars which are not variable, the mean should be calculated from the data after data reduction is completed, but before detrending is performed. This mean should then be added to the detrended data. However, calculating the mean from the calibrated data does not return the most accurate magnitude value, because of the values from the bRing database mentioned in \ref{sec:discdatared}.

Stars with no known periods were assumed to be non-variable stars and detrended as such. Possible undiscovered periods can be found by using the data available before detrending.
%
Variable stars with a period longer than 500 days were not detrended for their period. If an eclipse is visible in the light curve, it can only show up for a maximum of one time, which means detrending would not have an effect.
%
Pulsating stars with a period below one day were also detrended as non-variable stars. These short periods of a few hours are not visible in the Lomb-Scargle periodograms. The true period could be dominated by systematic effects within one day which cause stronger signals. This is because after detrending, periodic signals of a fraction of a day still remain. Periodic signals of a multiple of one day still remain as well. These signals should be handled carefully when searching for variability in a light curve.
%
No detrending was conducted for the sidereal period of the moon, which is about 27.3 days. This peak is very rarely observed in periodograms. If this peak is still found, it should be treated especially carefully, because we did not remove this signal in the detrending process.

@@

The light curves of the two brightest stars in our data set, Canopus (\ref{Canopus}) and Rigil Kentaurus (\ref{Rigil_Kentaurus}), contain bright peaks of scattered data points. This could be the result of overcorrecting the data affected by clouds, since these peaks occur mostly at very cloudy days.

In the light curve of Hadar (\ref{Hadar}) the brightness seems to fade at the end of a block of data, directly before the star is not visible for a few months. This dip in brightness is probably caused by a lack of calibration. For several stars, it seems the first and last few days of data should be removed because of this inaccuracy.

@@

\subsection{Future research}
In the future, the data reduction of the bright stars should be perfected. There are still a few errors in the data which should be fixed. For example, some invalid values remain.

The bRing cameras collect new raw data every day. This means that more calibration will be needed to polish the data collected after this research.

For the first time, long-term light curves have been made for stars brighter than magnitude 4. The light curves produced in this research can be used to determine variability in bright stars' emission by searching for periodic signals. The periodic signals discovered in the bRing data can be studied in more detail using different telescopes.

Furthermore, the shapes of the periods of variable stars brighter than magnitude 4 can now be made visible in a period folded light curve. This could tell us more about the properties of these variable stars.

Moreover, fake transit signals could be inserted in the light curves to determine the boundary conditions of a detectable exoplanet.

\section{Conclusion}
\label{sec:conclusion}
For the first time, long-term light curves for the 157 brightest stars ($m_V < 4$) in the southern hemisphere ($\delta \leq -30^o$) were created.
The data was collected by the bRing cameras, after which data reduction and detrending was applied. After the calibration, a search for periodic signals in the light curves was conducted. For six variable stars, the periods were found: 
\begin{itemize}
    \item Beta Doradus, a Delta Cephei with a period of $9.84 \pm 0.09$ days.
    \item Zeta Phoenicis, an eclipsing binary with a period of $1.670 \pm 0.002$ days.
    \item Alpha Doradus, a rotating star with a period of $2.943 \pm 0.008$ days.
    \item L Carinae, a Delta Cephei with a period of $35.6 \pm 1.2$ days.
    \item Mu$^1$ Scorpii, a Beta Lyrae-type eclipsing binary with a period of $1.446 \pm 0.002$ days.
    \item Delta Velorum, an eclipsing binary with a period of $45.2 \pm 2.0$ days.
\end{itemize}
The light curves are most suitable for finding variability in the stars' emissions, especially for long periods ($>$ 1 day). The light curves produced in this research could lead to the discovery of exoplanets or stellar companions around the brightest stars in the sky.

@@

   \begin{enumerate}
      \item asdf
      \item asdf
   \end{enumerate}

@@

>>>>

% added to hide columns in the tables
\usepackage{array}
\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}

\usepackage{appendix}

% align columns in table
\usepackage{makecell}

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {The brightest stars in the sky are also amongst the most difficult to obtain long-term precision photometry. }
  % aims heading (mandatory)
   {We provide high cadence light curves with an individual photometric precision of 0.5\% for 157 stars in the Southern hemisphere from the bRing robotic observatories.}
  % methods heading (mandatory)
   {We process the bRing images and remove the systematic trends due to the large pixel sizes, the varying night sky background, cloud coverage and intrapixel variations, in addition to diurnal, synodic and seasonal variations.}
  % results heading (mandatory)
   {We present 154 light curves for stars $m_V<4$ for all stars below $\delta \leq -30\degr $ covering baselines up to 3 years. The data is obtained by the $\beta$ Pictoris b Ring project (bRing), after which it is reduced and detrended.}
  % conclusions heading (optional), leave it empty if necessary 
   {}

@@

\begin{enumerate}
    \item All data points from the eastern Australian camera on 3 and 4 April 2018 and the eastern South African camera on 10 September 2020 were discarded due to significant outliers of unknown origin.
    \item The 2.35 second exposures were used.
    %\item The data points where the cloud error was 3$\sigma$ above the mean cloud error were deleted.
    %
    %The 3$\sigma$ cutoff was estimated by eye.
    %
    %The cloud error tells us how the transmission changes over time; a big change might mean a cloud is in view.
    %
    %These outliers usually indicate that the clouds are variable at that point in time, in which case the data should not be used.
    \item The 3$\sigma$ outliers of the clouds were removed. %This results in less background noise.
    \item The 5$\sigma$ outliers of the sky background were rejected. %This rejection also results in less background noise.
    \item The 5$\sigma$ outliers based on magnitude error were discarded. %A big error could mean that the measurement is wrong.     
    \item All data where the Sun is lower than $-18\degr$ was selected. %This was added to ensure that the sky background did not get too bright.     
    \item We made sure that the magnitude error for the daily data is always greater than zero and finite, so no incorrect values are encountered. 
    \item We used the astrometry and photometry flags of the daily data. 
    %
    These tell us if the measured flux is too high or too low to be realistic or if no photometry was performed due to, e.g., the star being too close to the edge of the image.
    %
    Only the data without any bad flags was used. 
\end{enumerate}

@@

@@

The last trend we removed is the one caused by the moon, which changes the sky background.
%
Trends matched to the synodic period (29.5306 days) were fitted and removed.
%
At this stage, the light curve for each star has all known trends removed.
%
For variable stars with a known period, we removed the large amplitude periodic variations before carrying out the detrending listed above, and then added this offset back into the light curve after the reduction steps.
%
Examples of the detrending steps are shown in the figures below.

XXXX wait for detrendsteps_plot.py

@@

\section{Results}
\label{sec:results}

@@

XXX in a Rosa email what are the numbers

message://%3c1131158490.6158.1695733941581@mail.ziggo.nl%3e

I believe the HR-diagram was indeed made with Gaia data.

In order to make the plots in the ``Representative light curves'' section, we could use the makelightcurve.py script that we shared before. You will only have to alter the number all the way at the bottom of the script in "plotLightCurve", which has to be the ASCC number of the star that you want to plot.

These are the stars and their ASCC numbers that you requested:

The brightest star we have: Canopus: ASCC 2111805
Delta Pavonis: ASCC 2424942
Two interesting variable stars: zeta Phoenicis, eclipsing binary: ASCC 2198437
and l Carinae, cepheid: ASCC 2311128

Attached are the code for the reduction-steps plot and the HR-diagram.

@@

%\begin{enumerate}
% \item \ref{Canopus} shows the light curve of alpha Carinae, the second brightest star in the sky and the brightest star in the southern hemisphere. It is better known as Canopus. The light curve can be seen in.
% \item \ref{Rigil_Kentaurus} shows the light curve of alpha Centauri A, the third brightest stars in the sky. It is also known as Rigil Kentaurus. It is part of the alpha Centauri system, which contains Proxima Centauri, the closest star known to the Sun. 
% \item \ref{Achernar} presents the light curve of alpha Eridani, also known as Achernar.
% \item \ref{Hadar} shows the light curve of beta Centauri, also called Hadar. This star is a Beta Cephei.
% \item \ref{Acrux} presents the light curve of alpha Crucis, a binary star system also known as Acrux.
% \item \ref{Mimosa} shows the light curve of beta Crucis, also known as Mimosa.
% \item \ref{Shaula} shows the light curve of lambda Scorpii, also known as Shaula. This is a binary system, with a Beta Cephei as primary star.
% \item \ref{Gacrux} displays the light curve of gamma Crucis, also called Gacrux.
% \item \ref{Miaplacidus} shows the ninth brightest star, beta Carinae. It is also known as Miaplacidus.
% \item \ref{Alnair} shows the final brightest star. This is alpha Gruis, also known as Alnair.

@@

Two stars are very close to the Sun in the HR diagram in \ref{HRD}.
%
These stars are delta Pavonis and Beta Hydri.
%
Delta Pavonis has a luminosity of 1.22 L$_\odot$ \citep{Bruntt_2010}, a mass of 0.991 M$_\odot$ and a radius of 1.22 R$_\odot$ \citep{2008yCat..21680297T}.
%
It is a subgiant star which will relatively soon start to become a red giant.
%
Beta Hydri has a luminosity of 3.49 L$_\odot$, a mass of 1.08 M$_\odot$ and a of radius 1.81 R$_\odot$ \citep{Brand_o_2011}.
%
Beta Hydri is also a subgiant star.

@@

\section{Discussion}

\label{sec:discussion}

157 light curves of the brightest stars ($m_V < 4$) in the southern hemisphere ($\delta \leq -30^o$) were created.
%
This is the first time light curves have been produced for such bright stars.
%
We discuss our results in the subsections below. 
%
Limitations and strengths of the methods used are given as well.

\subsection{Data reduction}

\label{sec:discdatared}
% The data reduction still has a few shortcomings.

@@

Intrapixel variations were neglected in the data reduction.
%
These quasi-sinusoidal modulations are caused by the interline design of the CCDs \citep{Talens_2018}.
%
The intrapixel variations cause noise in the light curves, but are too complex to remove in this research.

@@

After detrending the calibrated data, the mean magnitude of the stars is zero.
%
For variable stars this is prevented by adding the offset of the period back into the detrended data.
%
To fix the mean for the stars which are not variable, the mean should be calculated from the data after data reduction is completed, but before detrending is performed.
%
This mean should then be added to the detrended data.
%
However, calculating the mean from the calibrated data does not return the most accurate magnitude value, because of the values from the bRing database mentioned in \ref{sec:discdatared}.

Stars with no known periods were assumed to be non-variable stars and detrended as such.
%
Possible undiscovered periods can be found by using the data available before detrending.
%
Variable stars with a period longer than 500 days were not detrended for their period.
%
If an eclipse is visible in the light curve, it can only show up for a maximum of one time, which means detrending would not have an effect.
%
Pulsating stars with a period below one day were also detrended as non-variable stars.
%
These short periods of a few hours are not visible in the Lomb-Scargle periodograms.
%
The true period could be dominated by systematic effects within one day which cause stronger signals.
%
This is because after detrending, periodic signals of a fraction of a day still remain.
%
Periodic signals of a multiple of one day still remain as well.
%
These signals should be handled carefully when searching for variability in a light curve.
%
No detrending was conducted for the sidereal period of the moon, which is about 27.3 days.
%
This peak is very rarely observed in periodograms.
%
If this peak is still found, it should be treated especially carefully, because we did not remove this signal in the detrending process.

@@

%The light curves of the two brightest stars in our data set, Canopus (\ref{Canopus}) and Rigil Kentaurus (\ref{Rigil_Kentaurus}), contain bright peaks of scattered data points. This could be the result of overcorrecting the data affected by clouds, since these peaks occur mostly at very cloudy days.

%In the light curve of Hadar (\ref{Hadar}) the brightness seems to fade at the end of a block of data, directly before the star is not visible for a few months. This dip in brightness is probably caused by a lack of calibration. For several stars, it seems the first and last few days of data should be removed because of this inaccuracy.

@@

\subsection{Future research}

In the future, the data reduction of the bright stars should be perfected.
%
There are still a few errors in the data which should be fixed.
%
For example, some invalid values remain.

For the first time, long-term light curves have been made for stars brighter than magnitude 4.
%
The light curves produced in this research can be used to determine variability in bright stars' emission by searching for periodic signals, which can then be matched up with other observations.
%
%The periodic signals discovered in the bRing data can be studied in more detail using different telescopes.

The shapes of the periods of variable stars brighter than magnitude 4 can now be made visible in a period folded light curve.

@@

\label{sec:conclusion}

We have produced detrended light curves for 157 stars $(M_V<4)$ that are visible from the Southern bRing stations ($\delta \leq -30^o$).
%
These light curves cover over seven years of high cadence photometry, enabling frequency domain studies over seven decades of timescales.
%
The light curves are suitable for pulsational studies and several time domain cases.
%
All data and data reduction scripts are available online.

@@

\begin{appendix}
In the table below, the following information is given for all 157 stars, from left to right: ASCC- number, HD identifier, V-magnitude according to the bRing catalogue, and the period which was used for detrending in days. The stars are ordered by ASCC-number.
\newpage
\begin{table*}[h]
\centering
\begin{tabular}{|l|l|l|l|HHHHl|}
\hline
\textbf{ASCC}    & \textbf{HD}    & \textbf{Names} & \boldmath$m_V$  & \textbf{AUW}    & \textbf{AUE}    & \textbf{SAW}    & \textbf{SAE}   & \textbf{Period}     \\ \hline
\hline
1721367 & 27376 & upsilon$^4$ Eridani & 3.546 & 42029 & 71155 & 33430 & 77722 & - \\ \hline 
1722082 & 29291 & \makecell[l]{Theemin,\\ upsilon$^2$ Eridani}  & 3.805 & 19570 & 1873 & 15334 & 25559 & - \\ \hline 
1728196 & 44402 & \makecell[l]{Furud,\\ zeta Canis Majoris}  & 3.009 & 26425 & 4937 & 18505 & 25486 & - \\ \hline 
1728326 & 44762 & delta Columbae & 3.841 & 47741 & 42160 & 30414 & 57096 & - \\ \hline 
1730728 & 50013 & kappa Canis Majoris & 3.516 & 45017 & 37468 & 28910 & 54554 & - \\ \hline 
1748375 & 74575 & alpha Pyxidis & 3.68 & 43115 & 41415 & 41515 & 51432 & - \\ \hline 
1762319 & 100407 & xi Hydrae & 3.535 & 35249 & 18853 & 43602 & 43095 & - \\ \hline 
1776717 & 141556 & chi Lupi & 3.956 & 44910 & 70143 & 74660 & 67749 & - \\ \hline 
1781002 & 151680 & \makecell[l]{Larawag,\\ epsilon Scorpii} & 2.259 & 34210 & 45114 & 59976 & 54262 & - \\ \hline 
1790528 & 165135 & \makecell[l]{Alnasl,\\ gamma$^2$ Sagittarii} & 3.239 & 22639 & 11112 & 38527 & 32720 & - \\ \hline 
1821588 & 36597 & epsilon Columbae & 3.862 & 63601 & 95234 & 48186 & 91536 & - \\ \hline 
1822707 & 39425 & \makecell[l]{Wazn,\\ beta Columbae} & 3.105 & 70354 & 99644 & 54385 & 103205 & - \\ \hline 
1831780 & 63032 & c Puppis & 3.621 & 95254 & 120484 & 172314 & 137767 & - \\ \hline 
1839751 & 74006 & beta Pyxidis & 3.96 & 67463 & 81382 & 74510 & 92615 & - \\ \hline 
1862167 & 115892 & iota Centauri & 2.743 & 73709 & 106510 & 141952 & 113897 & - \\ \hline 
1862828 & 117440 & d Centauri & 3.232 & 82682 & 124294 & 166321 & 142042 & - \\ \hline 
1865291 & 123139 & \makecell[l]{Menkent,\\ theta Centauri} & 2.058 & 71728 & 109034 & 114756 & 108006 & - \\ \hline 
1867878 & 129116 & beta Centauri & 3.99 & 84913 & 132249 & 219105 & 146755 & - \\ \hline 
1871021 & 136422 & phi$^1$ Lupi & 3.568 & 67560 & 111915 & 135354 & 110184 & - \\ \hline 
1873533 & 143118 & eta Lupi & 3.414 & 87890 & 150376 & 237593 & 155971 & - \\ \hline 
1875903 & 151890 & \makecell[l]{Xamidimura,\\ mu$^1$ Scorpii} & 2.993 & 80328 & 151181 & 207641 & 144973 & 1.44626907 \\ \hline 
1875934 & 151985 & \makecell[l]{Pipirima,\\ mu$^2$ Scorpii} & 3.548 & 80034 & 150489 & 204726 & 144387 & - \\ \hline 
1880579 & 158408 & \makecell[l]{Lesath,\\ upsilon Scorpii} & 2.674 & 69112 & 134756 & 149201 & 122917 & - \\ \hline 
1880898 & 158926 & \makecell[l]{Shaula,\\ lambda Scorpii} & 1.623 & 58209 & 114228 & 81739 & 129014 & - \\ \hline 
1881897 & 160578 & kappa Scorpii & 2.381 & 86734 & 190031 & 182930 & 168445 & - \\ \hline 
1882798 & 161892 & \makecell[l]{Fuyue,\\ G Scorpii} & 3.183 & 64900 & 138398 & 147147 & 129589 & - \\ \hline 
1887460 & 167618 & eta Sagittarii & 3.131 & 60904 & 133603 & 123343 & 122620 & - \\ \hline 
1901232 & 207971 & \makecell[l]{Aldhanab,\\ gamma Gruis} & 3.003 & 58252 & 128824 & 94915 & 126457 & - \\ \hline 
1905964 & 2262 & kappa Phoenicis & 3.871 & 130543 & 275229 & 136936 & 334749 & - \\ \hline 
1905967 & 2261 & \makecell[l]{Ankaa,\\ alpha Phoenicis} & 2.391 & 125364 & 261656 & 126294 & 337648 & - \\ \hline 
1907532 & 9053 & gamma Phoenicis & 3.44 & 134345 & 278078 & 119534 & 377143 & - \\ \hline 
1909803 & 18622 & theta$^1$ Eridani & 3.211 & 57635 & 126153 & 55993 & 138132 & - \\ \hline 
1911993 & 26967 & alpha Horologii & 3.854 & 151370 & 255602 & 115967 & 360956 & - \\ \hline 
1923547 & 59717 & \makecell[l]{Hadir,\\ sigma Puppis} & 3.26 & 171044 & 231000 & 170738 & 334356 & - \\ \hline 
1925996 & 64440 & a Puppis & 3.709 & 163970 & 218126 & 170931 & 210093 & - \\ \hline 
\end{tabular}
\end{table*}

\newpage

\begin{table*}[h]
\centering
\begin{tabular}{|l|l|l|l|HHHHl|}
\hline
\textbf{ASCC}    & \textbf{HD}    & \textbf{Names} & \boldmath$m_V$  & \textbf{AUW}    & \textbf{AUE}    & \textbf{SAW}    & \textbf{SAE}   & \textbf{Period}     \\ \hline
\hline
1927667 & 66811 & \makecell[l]{Naos,\\ zeta Puppis} & 2.217 & 115762 & 217775 & 123059 & 186477 & - \\ \hline 
1936013 & 78647 & \makecell[l]{Suhail,\\ lambda Velorum} & 2.21 & 134666 & 193189 & 162463 & 334359 & - \\ \hline 
1938697 & 82434 & psi Velorum & 3.582 & 158426 & 201176 & 217702 & 201720 & - \\ \hline 
1943462 & 88955 & q Velorum & 3.832 & 173251 & 199234 & 227958 & 305305 & - \\ \hline 
1959119 & 120307 & nu Centauri & 3.397 & 167311 & 208245 & 262723 & 291221 & - \\ \hline 
1959126 & 120324 & mu Centauri & 3.46 & 171644 & 212955 & 267756 & 339768 & - \\ \hline 
1959843 & 121743 & phi Centauri & 3.811 & 167053 & 214406 & 262361 & 340358 & - \\ \hline 
1959875 & 121790 & upsilon$^1$ Centauri & 3.848 & 181713 & 229943 & 277109 & 365521 & - \\ \hline 
1962822 & 127972 & eta Centauri & 2.328 & 145080 & 194372 & 183128 & 339904 & - \\ \hline 
1964703 & 132058 & beta Lupi & 2.668 & 164615 & 206248 & 221732 & 354055 & - \\ \hline 
1967127 & 136298 & delta Lupi & 3.206 & 152168 & 205969 & 244678 & 235667 & - \\ \hline 
1967246 & 136504 & epsilon Lupi & 3.369 & 176363 & 240548 & 274742 & 377785 & - \\ \hline 
1968585 & 138690 & gamma Lupi & 2.812 & 153114 & 217706 & 231582 & 261977 & - \\ \hline 
1974877 & 152334 & zeta$^1$ Scorpii & 3.608 & 153031 & 246511 & 226171 & 319588 & - \\ \hline 
1976808 & 155203 & eta Scorpii & 3.315 & 153548 & 264762 & 241674 & 393034 & - \\ \hline 
1980004 & 159532 & \makecell[l]{Sargas,\\ theta Scorpii} & 1.851 & 96750 & 157836 & 127172 & 383352 & - \\ \hline 
1981329 & 161471 & iota$^1$ Scorpii & 3.005 & 111101 & 242913 & 219947 & 224807 & - \\ \hline 
1992514 & 181454 & \makecell[l]{Arkab Prior,\\ beta$^1$ Sagittarii} & 3.953 & 149254 & 275843 & 224579 & 357822 & - \\ \hline 
1992594 & 181869 & \makecell[l]{Rukbat,\\ alpha Sagittarii} & 3.95 & 122340 & 243233 & 194315 & 242710 & - \\ \hline 
2000576 & 213009 & delta$^1$ Gruis & 3.959 & 133316 & 271688 & 168182 & 356114 & - \\ \hline 
2003304 & 496 & epsilon Phoenicis & 3.875 & 129175 & 286752 & 135224 & 347961 & - \\ \hline 
2004703 & 6595 & beta Phoenicis & 3.315 & 148123 & 303550 & 147342 & 418886 & - \\ \hline 
2005323 & 9362 & delta Phoenicis & 3.937 & 149132 & 309775 & 155544 & 434821 & - \\ \hline 
2021081 & 63922 & P Puppis & 3.941 & 191324 & 241883 & 204760 & 375992 & - \\ \hline 
2023562 & 68273 & gamma$^2$ Velorum & 1.812 & 91755 & 180554 & 88358 & 407483 & - \\ \hline 
2027459 & 74180 & b Velorum & 3.808 & 200293 & 246277 & 223264 & 379316 & - \\ \hline 
2028223 & 75063 & a Velorum & 3.89 & 200295 & 236193 & 243967 & 371324 & - \\ \hline 
2030506 & 78004 & c Velorum & 3.743 & 200714 & 253268 & 241167 & 394426 & - \\ \hline 
2040152 & 92139 & p Velorum & 3.832 & 211973 & 248356 & 277991 & 395668 & - \\ \hline 
2041127 & 93497 & mu Velorum & 2.709 & 191569 & 242702 & 259890 & 400629 & - \\ \hline 
2050494 & 109787 & tau Centauri & 3.845 & 199681 & 246063 & 292914 & 403599 & - \\ \hline 
2050813 & 110304 & gamma Centauri & 2.421 & 108758 & 169885 & 129350 & 378054 & - \\ \hline 
2056697 & 121263 & zeta Centauri & 2.523 & 155149 & 212851 & 217055 & 380046 & - \\ \hline 
2058847 & 125238 & iota Lupi & 3.542 & 188185 & 246938 & 299346 & 399890 & - \\ \hline 
2061037 & 129056 & alpha Lupi & 2.282 & 122046 & 188434 & 173599 & 400435 & - \\ \hline 
2064147 & 134481 & kappa Lupi & 3.848 & 190900 & 269035 & 311192 & 454330 & - \\ \hline 
2079242 & 158427 & alpha Arae & 2.835 & 181564 & 299495 & 283008 & 497554 & - \\ \hline 
2086192 & 169467 & alpha Telescopii & 3.482 & 166337 & 293712 & 264261 & 452607 & - \\ \hline 
2094623 & 196171 & alpha Indi & 3.104 & 142117 & 279285 & 209775 & 420754 & - \\ \hline 
2098110 & 209952 & \makecell[l]{Alnair,\\ alpha Gruis} & 1.763 & 75698 & 170034 & 101517 & 437843 & - \\ \hline 
2099216 & 214952 & \makecell[l]{Tiaki,\\ beta Gruis} & 2.114 & 97692 & 234739 & 97476 & 421217 & - \\ \hline 
2100006 & 218670 & iota Gruis & 3.878 & 136272 & 279562 & 165335 & 400079 & - \\ \hline 
\end{tabular}
\end{table*}

\newpage

\begin{table*}[h]
\centering
\begin{tabular}{|l|l|l|l|HHHHl|}
\hline
\textbf{ASCC}    & \textbf{HD}    & \textbf{Names}                  & \boldmath$m_V$  & \textbf{AUW}    & \textbf{AUE}    & \textbf{SAW}    & \textbf{SAE}   & \textbf{Period}     \\ \hline
\hline
2104402 & 14228 & phi Eridani & 3.546 & 152455 & 317682 & 148180 & 444632 & - \\ \hline 
2110269 & 39060 & beta Pictoris & 3.851 & 175652 & 272185 & 172186 & 420967 & - \\ \hline 
2111805 & 45348 & \makecell[l]{Canopus,\\ alpha Carinae} & -0.64 & 29 & 545 & 1571 & 60898 & - \\ \hline 
2113099 & 50310 & \makecell[l]{Altaleban,\\ tau Puppis} & 2.93 & 185365 & 284208 & 195685 & 428269 & - \\ \hline 
2117254 & 65575 & chi Carinae & 3.448 & 216554 & 279097 & 236114 & 434479 & - \\ \hline 
2119926 & 74195 & omicron Velorum & 3.588 & 216834 & 286216 & 199237 & 437295 & - \\ \hline 
2120290 & 74956 & delta Velorum & 1.968 & 82402 & 200637 & 129889 & 439146 & 45.15 \\ \hline 
2129944 & 86440 & phi Velorum & 3.533 & 227038 & 276556 & 277796 & 445705 & - \\ \hline 
2141153 & 98718 & pi Centauri & 3.884 & 230878 & 253979 & 308891 & 424507 & - \\ \hline 
2146573 & 105435 & delta Centauri & 2.558 & 167581 & 220369 & 216269 & 385182 & - \\ \hline 
2146914 & 105937 & rho Centauri & 3.954 & 222601 & 249041 & 309345 & 416426 & - \\ \hline 
2148632 & 108483 & sigma Centauri & 3.903 & 211649 & 252105 & 299710 & 411859 & - \\ \hline 
2154691 & 118716 & epsilon Centauri & 2.272 & 119054 & 186701 & 166476 & 406334 & - \\ \hline 
2162355 & 134505 & zeta Lupi & 3.398 & 214278 & 298075 & 351660 & 474895 & - \\ \hline 
2182568 & 165024 & theta Arae & 3.664 & 183731 & 312778 & 302575 & 496629 & - \\ \hline 
2195224 & 215789 & epsilon Gruis & 3.48 & 146373 & 328673 & 194265 & 479643 & - \\ \hline 
2198437 & 6882 & \makecell[l]{Wurren,\\ zeta Phoenicis} & 3.977 & 157643 & 329094 & 166608 & 470090 & 1.6697671 \\ \hline 
